---
title: "Simulations with SPsimSeq"
author: "Enrico Gaffo"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
params:
  outdir: "IPF_sims"
  input_dataset_bjr_file: "../data/IPF_unfiltered_CirComPara2_circbjr.csv"
  input_dataset_meta_file: "../data/IPF_meta.csv"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# params <- list(input_dataset_bjr_file = "../data/IPF_unfiltered_CirComPara2_circbjr.csv", 
#                input_dataset_meta_file = "../data/IPF_meta.csv", 
#                outdir = "IPF_sims")

# load required libraries
library(data.table)

library(ggplot2)
library(pheatmap)
library(viridis)
library(scales)

library(DT)

# install.packages("devtools", Ncpus = 12)
# library(devtools)
# install_github("CenterForStatistics-UGent/SPsimSeq", Ncpus = 12)
library(SPsimSeq)

library(edgeR)
library(DESeq2)
library(BiocParallel)

# install.packages("qs", Ncpus = 24)
library(qs)

dir.create(path = params$outdir, showWarnings = F, recursive = T)
```

# The source data set

Load the original data and make a basic filtering  

```{r}
# load the original data
# input_dataset_bjr_file <- "../data/ALZ_unfiltered_CirComPara2_circbjr.csv"
# input_dataset_meta_file <- "../data/ALZ_meta.csv"

counts_mt <- as.matrix(data.frame(fread(params$input_dataset_bjr_file), 
                                  row.names = "circ_id"))
group_dt <- fread(params$input_dataset_meta_file)
group_df <- data.frame(group_dt, 
                       row.names = "sample_id")
```

Data have `r nrow(counts_mt)` circRNAs.  

Samples partitioned between conditions  

```{r}
cond_parts <- group_dt[, .N, by = condition][, Frac := N/sum(N)][]
cond_parts
```

```{r}
min_samples <- 3
# remove genes with insufficient expression (important step to avoid bugs)
counts_mt <- counts_mt[rowSums(counts_mt > 0) >= min_samples, ]
```

Filtered data have `r nrow(counts_mt)` circRNAs (BJR > 0 in at least `r min_samples` samples).  

```{r}
lib_sizes <- apply(counts_mt, 2, sum)[rownames(group_df)]
lib_size_dt <- data.table(group_df, 
                          Lib_size = lib_sizes, 
                          keep.rownames = "Sample")

plot_dt <- lib_size_dt
plot_dt$Sample <- factor(plot_dt$Sample, 
                         levels = plot_dt[order(Lib_size), Sample],
                         ordered = T)

ggplot(plot_dt,
       aes(x = Sample, y = Lib_size)) +
  geom_col() +
  facet_grid(cols = vars(condition), space = "free_x", drop = T, scales = "free_x") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
ggplot(plot_dt,
       aes(x = condition, y = Lib_size)) +
  geom_boxplot(varwidth = T) +
  geom_point(shape = 21)
```

```{r}
seed.num <- 2021
set.seed(seed.num)
```

## Library size of samples

```{r}
## compute sample similarity according to library size
sample_clust_by_libsize <- 
  hclust(d = dist(x = lib_sizes, method = "euclidean"), 
         method = "complete")

Nclust_libsize <- 4
```

```{r, fig.height=7.5, fig.width=4.5}
pheatmap(mat = as.matrix(lib_sizes), 
         scale = "none", 
         color = viridis(255),
         cluster_rows = sample_clust_by_libsize, 
         cluster_cols = F, 
         cutree_rows = Nclust_libsize, 
         cellwidth = 9, cellheight = 9, 
         annotation_row = group_df)
```

```{r}
sample_libsize_clust_dt <- 
  merge(data.table(Sample = sample_clust_by_libsize$labels, 
                   Corder = sample_clust_by_libsize$order,
                   LibGroup = cutree(tree = sample_clust_by_libsize, 
                                     k = Nclust_libsize)),
        lib_size_dt,
        by = "Sample")

ggplot(sample_libsize_clust_dt,
       aes(x = factor(LibGroup), y = Lib_size, color = condition)) +
  geom_boxplot(varwidth = T) +
  geom_jitter(position = position_dodge2(width = .5), shape = 1)
```

```{r}
datatable(sample_libsize_clust_dt[, .(Nsamples = .N,
                            MaxLibSize = max(Lib_size),
                            MinLibSize = min(Lib_size)), 
                        by = .(LibGroup, condition)][order(LibGroup, condition)],
          rownames = F, filter = "top")
```

# Simulate datasets

## Prepare the source data set 

Select samples of similar library size from the original data set

```{r}
## subset original matrix using samples of similar library size
sample_subset <- sample_libsize_clust_dt[!LibGroup %in% c(), Sample] ## NB: no filter!!
## subset sample metadata 
sample_table <- group_df[sample_subset, "condition", drop = F]

orig_mat <- counts_mt[, sample_subset]
## only for testing
# orig_mat <- orig_mat[, data.table(sample_table, keep.rownames = "Sample")[, head(.SD, 5), by = condition][, Sample]]

## keep circRNAs expressed in at least a fraction of the samples
min_samples <- floor(ncol(orig_mat) / 2) #3

# ## filter out circRNAs expressed in less than min_samples samples
# ## Also, we want at least 1 sample > 0 in each sample group
# cond_levels <- unique(sample_table$condition)
# 
# mat_cond1 <- orig_mat[, rownames(sample_table)[sample_table$condition == cond_levels[1]]]
# mat_cond2 <- orig_mat[, rownames(sample_table)[sample_table$condition == cond_levels[2]]]
# 
# keep <- 
#   unique(c(rownames(orig_mat)[rowSums(mat_cond1 > 0) > 0],
#            rownames(orig_mat)[rowSums(mat_cond2 > 0) > 0]))
# orig_mat <- orig_mat[keep, ]

orig_mat <- orig_mat[rowSums(orig_mat > 0) >= min_samples, ]
```

`r dim(orig_mat)` circRNAs - samples in the fitered original data set.  

```{r}
## parameters to simulate the data sets
Ncircrnas <- min(nrow(orig_mat), 10000) #5000
```

CircRNAs were divided into 10 expression quantiles.  
`r Ncircrnas` to be simulated will be selected randomly but choosing `r floor(Ncircrnas / 10)` for each expression quantile.  

### Check library size after a first circRNA selection 

```{r}
plot_dt <- 
    merge(data.table(data.frame(LibSize = colSums(orig_mat)), 
                     keep.rownames = "SampleID"), 
          data.table(sample_table, 
                     keep.rownames = "SampleID"), 
          by = "SampleID")

plot_dt$SampleID <- factor(plot_dt$SampleID, levels = plot_dt[order(LibSize), SampleID], ordered = T)

ggplot(plot_dt, 
       aes(x = SampleID, y = LibSize, fill = condition)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1),
          legend.position = "top")
```

```{r}
ggplot(plot_dt, 
       aes(x = condition, y = LibSize, color = condition)) +
    geom_boxplot(varwidth = T, notch = F) +
    geom_point() +
    guides(color = guide_none()) +
    theme(legend.position = "top")
```

```{r}
## percentage of DECs
fracDECs <- 0.1
```

`r floor(Ncircrnas * fracDECs)` differentially expressed circRNAs will be simulated.  


### Save the source data set

```{r}
## save source dataset
orig_mat_dge <- edgeR::DGEList(counts = orig_mat, group = sample_table[colnames(orig_mat), "condition"])

source_dataset_qs <- file.path(params$outdir, "trimmed_source_dataset.qs")
qsave(x = orig_mat_dge, 
      file = source_dataset_qs, 
      nthreads = multicoreWorkers(), 
      preset = "fast")
```

The source data sets can be loaded from the <a href="`r source_dataset_qs`">`r source_dataset_qs`</a> R object using the <a href="https://cran.r-project.org/web/packages/qs/index.html">qs</a> package.  

## Set parameters to simulate the data sets

```{r}
# SPsimSeq simulation
SPsimSeq_simulate <- 
  function(params_list, ...) {

    seed.num <- 2021
    set.seed(seed.num)

    counts_mt <- params_list$counts_mt
    reps_per_group <- params_list$reps_per_group
    Ncircrnas <- params_list$Ncircrnas
    fracDECs <- params_list$fracDECs
    # circs_to_sim <- params_list$circs_to_sim
    group_df <- params_list$group_df
    model_zeros <- params_list$model_zeros
    n.sims <- params_list$n.sims
    cand_DE_genes <- NULL
    if(!is.null(params_list$cand_DE_genes)) {
      cand_DE_genes <- list(nonnull.genes = params_list$cand_DE_genes,
                            null.genes = rownames(counts_mt)[!rownames(counts_mt) %in%
                                                               params_list$cand_DE_genes])
    }
    w <- params_list$w
    
    # counts_mat <- counts_mt[circs_to_sim, ]
    counts_mat <- counts_mt
    
    sim_pars <- paste(n.sims, "data sets of", 
                      Ncircrnas, "circRNAs per", 
                      2 * reps_per_group, "samples, modelling zero probability",
                      model_zeros)
    
    start_time <- Sys.time()
    message(paste(start_time, "start SPsimSeq to simulate", 
                  sim_pars))
    
    simdatasets <- 
      SPsimSeq(n.sim = n.sims,
               s.data = counts_mat, 
               n.genes = Ncircrnas, 
               tot.samples = 2 * reps_per_group, 
               pDE = fracDECs, 
               cand.DE.genes = cand_DE_genes,
               group = as.integer(factor(group_df[colnames(counts_mat), ])), 
               group.config = c(.5, .5), # fixed to equal group sizes
               model.zero.prob = model_zeros,
               batch = rep(1, ncol(counts_mat)),
               batch.config = 1, 
               w = w,
               result.format = "list",
               return.details = TRUE,
               ...) 
    
    runtime <- difftime(Sys.time(), start_time, units = "s")
    message(paste("SPsimSeq took", runtime, "seconds"))
    
    list(Datasets = simdatasets,
         runtime = runtime)
  }
```

```{r}
## parameters to simulate the data sets
n.sims <- 30
```

### DE data sets

```{r}
## ---- DE data sets ----
params_list <- 
  list(counts_mt = orig_mat,
       Ncircrnas = Ncircrnas, 
       fracDECs = fracDECs,
       cand_DE_genes = NULL, #nonnull_circs_names,
       group_df = sample_table,
       w = 0.7,
       n.sims = n.sims)

bulk_sims_params <- 
  list(N03_bulk = c(params_list, reps_per_group =  3, model_zeros = FALSE),
       N05_bulk = c(params_list, reps_per_group =  5, model_zeros = FALSE),
       N10_bulk = c(params_list, reps_per_group = 10, model_zeros = FALSE))

# sice_sims_params <- 
#   list(N03_sice = c(params_list, reps_per_group =  3, model_zeros = TRUE),
#        N05_sice = c(params_list, reps_per_group =  5, model_zeros = TRUE),
#        N10_sice = c(params_list, reps_per_group = 10, model_zeros = TRUE))
```

### Not DE data sets

```{r}
## ---- no DE data sets ----
## use the single condition samples and set fraction of DECs = 0
mock_params_list <- 
  list(counts_mt = orig_mat, #mock_orig_mat,
       Ncircrnas = Ncircrnas, 
       fracDECs = 0,
       cand_DE_genes = NULL,
       group_df = sample_table, #mock_sample_table,
       w = 0.7,
       n.sims = n.sims)

mock_bulk_sims_params <- 
  list(N03_bulk_mock = c(mock_params_list, reps_per_group =  3, model_zeros = FALSE),
       N05_bulk_mock = c(mock_params_list, reps_per_group =  5, model_zeros = FALSE),
       N10_bulk_mock = c(mock_params_list, reps_per_group = 10, model_zeros = FALSE))

# mock_sice_sims_params <- 
#   list(N03_sice_mock = c(mock_params_list, reps_per_group =  3, model_zeros = TRUE),
#        N05_sice_mock = c(mock_params_list, reps_per_group =  5, model_zeros = TRUE),
#        N10_sice_mock = c(mock_params_list, reps_per_group = 10, model_zeros = TRUE))
```

## Do simulations

```{r}
## do simulations in parallel
ds_par_list <- 
  c(bulk_sims_params,
    mock_bulk_sims_params)
# sice_sims_params,
# mock_sice_sims_params
```

```{r}
sim_ds_list <-
  bplapply(ds_par_list,
           SPsimSeq_simulate,
           BPPARAM = MulticoreParam(workers = min(length(ds_par_list), 
                                                  multicoreWorkers())))
```

```{r}
## 'qs' is much quicker than 'saveRDS' !!
simulated_datasets_qs <- file.path(params$outdir, "trimmed_simulated_datasets.qs")
qsave(x = sim_ds_list, 
      file = simulated_datasets_qs, 
      nthreads = multicoreWorkers(), 
      preset = "fast")
```

The simulated data sets can be loaded from the <a href="`r simulated_datasets_qs`">`r simulated_datasets_qs`</a> R object using the <a href="https://cran.r-project.org/web/packages/qs/index.html">qs</a> package.  

# Session info

```{r}
sessionInfo()
```

