---
title: "Concordance at the top"
author: "Enrico Gaffo"
date: 'Compiled: `r format(Sys.Date(), "%d %B, %Y")`'
output:
  html_document:
    code_folding: hide
    df_print: kable
    number_sections: no
    theme: united
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

<style>
#TOC {
  top: 1%;
  opacity: 0.5;
}
#TOC:hover {
  opacity: 1;
}
</style>

```{r setup, include=FALSE}
current.dir = "."
outdir <- "CAT"
dir.create(path = outdir, showWarnings = F, recursive = T)

knitr::opts_chunk$set(echo = F, warning = F,
                      fig.path = file.path(outdir, "Figs/"), 
                      dev = c("png", "svglite", "pdf"))
# knitr::opts_chunk$set(echo = TRUE, fig.path = file.path(current.dir, "consinstency/"))
```

```{r message=FALSE, warning=FALSE}
library(data.table)
# library(qs) ## to fast saving the results

library(ggplot2)
library(viridis)
library(ggdendro)
library(dendsort)
library(scales)

library(ffpe) ## for the CATplot
library(pracma) ## for the trapezoidal function used to compute AUC

library(BiocParallel)

library(ggrastr)
library(patchwork)
library(gridGraphics)
library(seriation)
```

```{r}
#' m1, m2 are character strings with the name of the methods to intersect
#' dt is a sorted data.table of method scores, with 'Method' and 'Cid' columns, 
#' which are the name of the method's score and the circRNA identifier, respectively.
getCAT_dt <- function(m1, m2, dt, maxrank = 100) {
    
    data.table::data.table(method1 = m1, 
                           method2 = m2, 
                           ffpe::CATplot(vec1 = dt[Method == m1, Cid],
                                         vec2 = dt[Method == m2, Cid], 
                                         maxrank = maxrank, 
                                         make.plot = F))
}
```

# Method names

```{r}
method_types <- 
  data.table(Method = c("circMeta_Dt_PZT", "circMeta_Lc_PZT", "DESeq2_BP_WaT", 
                        "DESeq2_Dt_LRT", "DESeq2_Dt_WaT", "DESeq2_GP_LRT", 
                        "DESeq2_Lc_LRT", "DESeq2_Sc_LRT", "DESeq2_Zi_LRT", 
                        "DESeq2_ZW_LRT", "DEsingle_Dt_LRT", "edgeR_Dt_LRT", 
                        "edgeR_rbst_LRT", "edgeR_rbst_QFT", "edgeR_rbst50df_LRT", 
                        "edgeR_rbstEdf_LRT", "edgeR_rbstTMMswp_LRT", "edgeR_ZW_LRT", 
                        "limma_St_Vst", "lncDIFF_Dt_LRT", "MAST_CPM_LRT", 
                        "metagenomeSeq_Dt_EBT", "monocle_Dt_LRT", "NBID_Dt_LRT", 
                        "NBID_Sc_LRT", "NOISeqBIO_TMM_LRT", "PoissonSeq_Dt_TT", 
                        "ROTScpm_Dt_TLT", "SAMseq_Dt_TT", "seurat_Bim_LRT", 
                        "seurat_Dt_WLX", "voom_Dt_MFT", "voom_LF_MFT", 
                        "voom_Qn_MFT", "voom_Rb_MFT", "voom_Sp_MFT", 
                        "voom_ZW_MFT", "wilcoxon_TMM_WLX"),
             Type = c("Bulk RNA-seq", "Bulk RNA-seq", "Bulk RNA-seq", 
                      "Bulk RNA-seq", "Bulk RNA-seq", "Single cell / metagenome", 
                      "Single cell / metagenome", "Single cell / metagenome", "Single cell / metagenome", 
                      "Single cell / metagenome", "Single cell / metagenome", "Bulk RNA-seq", 
                      "Bulk RNA-seq", "Bulk RNA-seq", "Bulk RNA-seq", 
                      "Bulk RNA-seq", "Single cell / metagenome", "Single cell / metagenome", 
                      "Single cell / metagenome", "Bulk RNA-seq", "Single cell / metagenome", 
                      "Single cell / metagenome", "Single cell / metagenome", "Single cell / metagenome", 
                      "Single cell / metagenome", "Bulk RNA-seq", "Bulk RNA-seq", 
                      "Single cell / metagenome", "Bulk RNA-seq", "Single cell / metagenome", 
                      "Single cell / metagenome", "Bulk RNA-seq", "Single cell / metagenome",
                      "Bulk RNA-seq", "Bulk RNA-seq", "Bulk RNA-seq", 
                      "Single cell / metagenome", "Single cell / metagenome"),
             BaseMethod = c("circMeta", "circMeta", "DESeq2", 
                            "DESeq2", "DESeq2", "glmGamPoi", 
                            "DESeq2", "DESeq2", "DESeq2", 
                            "DESeq2", "DEsingle", "edgeR", 
                            "edgeR", "edgeR", "edgeR", 
                            "edgeR", "edgeR", "edgeR", 
                            "limma", "lncDIFF", "MAST", 
                            "metagenomeSeq", "monocle", "NBID", 
                            "NBID", "NOISeqBIO", "PoissonSeq", 
                            "ROTS", "SAMseq", "Seurat", 
                            "Seurat", "Voom", "Voom", 
                            "Voom", "Voom", "Voom", 
                            "Voom", "Wilcoxon"))
```

```{r}
#' A function to mimic the ggplot default palette
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

method_colors <- setNames(object = gg_color_hue(length(method_types$Method)), 
                          nm = sort(method_types$Method))

method_types_colors.dt <- 
  merge(data.table(data.frame(Color = method_colors), keep.rownames = "Method"), 
        method_types, 
        by = "Method")[, .(Color = head(Color, 1)), by = BaseMethod]

method_types_colors <- unlist(split(method_types_colors.dt$Color, 
                                    method_types_colors.dt$BaseMethod))
```

```{r, fig.width=2.5, fig.height=6.69}
plot_dt <- 
  melt(copy(method_types)[, c("Base", "Parameters", 
                              "Test") := tstrsplit(Method, "_")][, .(Method,
                                                                     Type,
                                                                     `Base tool` = BaseMethod,
                                                                     Parameters,
                                                                     Test)], 
                id.vars = c("Method", "Type"))

plot_dt$variable <- factor(plot_dt$variable, 
                           levels = levels(plot_dt$variable), 
                           ordered = T)

plot_base_method_color_text <-
  ggplot(plot_dt, 
         aes(y = Method, 
             x = variable, 
             color = Method)) +
  geom_text(aes(label = value), 
            size = 3) +
    scale_x_discrete(position = "bottom") +
  labs(x = NULL, y = NULL) +
  coord_cartesian(clip = "off") +
  scale_color_manual(values = method_colors, guide = "none") +
  theme_bw() +
  theme(axis.text.y = element_blank(),
        text = element_text(size = 10),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(), 
        strip.background = element_rect(fill = NA), 
        panel.spacing.y = unit(0.05, "lines"),
        panel.spacing.x = unit(.1, "lines"))

# plot_base_method_color_text

plot_base_method_color_text_rot <-
  ggplot(plot_dt, 
         aes(x = Method, 
             y = variable, 
             color = Method)) +
  geom_text(aes(label = value), 
            size = 3, angle = 90) +
    # scale_x_discrete(position = "bottom") +
  labs(x = NULL, y = NULL) +
  coord_cartesian(clip = "off") +
  scale_color_manual(values = method_colors, guide = "none") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(angle = 90, hjust = .5),
        text = element_text(size = 10),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(), 
        strip.background = element_rect(fill = NA), 
        panel.spacing.y = unit(0.05, "lines"),
        panel.spacing.x = unit(.1, "lines"))

# plot_base_method_color_text_rot
```

# Base tiles

```{r, fig.width=7, fig.height=4}
library(ggthemes)
plot_dt <- copy(method_types)

plot_base_method_type_tiles <-
  ggplot(plot_dt, 
         aes(y = Method, 
             x = "", fill = Type)) +
  geom_tile(color = "white", width = 0.9, height = 0.9, 
            size = .5) +
  labs(x = NULL, y = NULL) +
  scale_fill_manual(values = setNames(tableau_color_pal(palette = "Classic Purple-Gray 6")(2), #"Nuriel Stone"
                                      c("Bulk RNA-seq", "Single cell / metagenome"))) +
  guides(fill = guide_legend(title = "Method purpose", 
                             title.position = "left", 
                             title.hjust = .5)) +
  theme_dendro() +
  theme(legend.position = "bottom")

# plot_base_method_type_tiles
```

# Between method concordance at the top

```{r}
## data set names prefix
Datasets <- c("DM1", "IDC", "IPF","MS")

resDE_datasets <- sapply(Datasets,
                         function(d) fread(file = file.path(".", 
                                                            paste0(d, "_evaluations/pval_deind.csv.gz")), 
                                           showProgress = F),
                         simplify = F, USE.NAMES = T)

preds_dt <- 
  rbindlist(resDE_datasets, 
            use.names = T, 
            idcol = "DS")[, Cid := seq_along(preds), 
                          by = .(DS, Dataset,  
                                 Method)][order(preds, na.last = T), 
                                          .(DS = paste(DS, Dataset, sep = "_"),
                                            Cid, Method, preds)]

method_names <- sort(unique(preds_dt$Method))

preds_dt$Method <- factor(preds_dt$Method, 
                          levels = method_names, 
                          ordered = T)

# method_colors <- setNames(hue_pal()(length(method_names)), method_names)
```


```{r}
cats <- 
  rbindlist(bplapply(X = split(x = preds_dt, f = preds_dt$DS), 
                     FUN = function(dt){
                       
                       # m12 <- expand.grid(m1 = unique(dt$Method), 
                       #                    m2 = unique(dt$Method))
                       # ## remove method match with itself
                       # m12 <- m12[!m12$m1 == m12$m2,]
                       
                       ## CAT is symmetric, therefore we can exclude half the pairs
                       m12 <- data.table(t(combn(levels(dt$Method), m = 2)))
                       
                       rbindlist(mapply(getCAT_dt, 
                                        m1 = m12$V1, m2 = m12$V2, 
                                        MoreArgs = list(dt = dt, maxrank = 100), 
                                        SIMPLIFY = F))}, 
                     BPPARAM = MulticoreParam(workers = multicoreWorkers())), 
            use.names = T, idcol = "Dataset")

cats[, featFrac := rank / max(rank), by = .(Dataset, method1, method2)]
```


```{r}
## get the area under the CAT curve
aucats <- cats[, .(AUCAT = pracma::trapz(featFrac, concordance)), 
               by = .(Dataset, method1, method2)]

## mean AUCAT across all simulated data sets
maucats <- aucats[, .(MeanAUCAT = mean(AUCAT)), 
                  by = .(method1, method2)]

## mean AUCAT across simulated data sets per set size
ss_maucats <- aucats[, .(MeanAUCAT = mean(AUCAT)), 
                  by = .(method1, method2, 
                         SetSize = sub("[^_]+_([^_]+)_.*", "\\1", Dataset))]
```


```{r} 
## mean concordance score at each rank across all simulated data sets
mconc <- cats[, .(concordance = mean(concordance)), 
              by = .(method1, method2, featFrac)]

## AUCAT according to the rank mean concordance
## NB: attach a new column (with redundant values) to ease later plotting
mconc[, AUCAT := trapz(featFrac, concordance), 
      by = .(method1, method2)]
```


```{r} 
## mean concordance score at each rank across simulated data sets per set size
ss_mconc <- cats[, .(concordance = mean(concordance)), 
                 by = .(method1, method2, featFrac, 
                        SetSize = sub("[^_]+_([^_]+)_.*", "\\1", Dataset))]

## AUCAT according to the rank mean concordance
## NB: attach a new column (with redundant values) to ease later plotting
ss_mconc[, AUCAT := trapz(featFrac, concordance), 
      by = .(method1, method2, SetSize)]
```

```{r} 
## compose a matrix for clustering and heatmap plotting
maucats_mat <- as.matrix(data.frame(dcast(maucats,
                                          method1 ~ method2, 
                                          value.var = "MeanAUCAT", 
                                          drop = F,
                                          fill = NA), 
                                    row.names = "method1"))

## N.B. only the upper/lower tringular of the matrix is
maucats_mat <- maucats_mat[sort(rownames(maucats_mat)),
                           sort(colnames(maucats_mat))]

## add NA diagonal
cnames <- c(setdiff(rownames(maucats_mat), colnames(maucats_mat)), colnames(maucats_mat))
rnames <- c(rownames(maucats_mat), setdiff(colnames(maucats_mat), rownames(maucats_mat)))

maucats_mat <- cbind(rep(NA, nrow(maucats_mat)),
                     maucats_mat)
maucats_mat <- rbind(maucats_mat,
                     rep(NA, ncol(maucats_mat)))

colnames(maucats_mat) <- cnames
rownames(maucats_mat) <- rnames
# dim(maucats_mat)

maucats_mat[lower.tri(maucats_mat, diag = F)] <- t(maucats_mat)[lower.tri(maucats_mat, diag = F)]

## just check everything is ok
# isSymmetric(maucats_mat)
```

```{r} 
## compose a matrix for clustering and heatmap plotting
n05ss_maucats_mat <- as.matrix(data.frame(dcast(ss_maucats[SetSize == "N05"],
                                                method1 ~ method2, 
                                                value.var = "MeanAUCAT", 
                                                drop = F,
                                                fill = NA), 
                                          row.names = "method1"))

## N.B. only the upper/lower tringular of the matrix is
n05ss_maucats_mat <- n05ss_maucats_mat[sort(rownames(n05ss_maucats_mat)),
                                       sort(colnames(n05ss_maucats_mat))]

## add NA diagonal
n05ss_cnames <- c(setdiff(rownames(n05ss_maucats_mat), colnames(n05ss_maucats_mat)), colnames(n05ss_maucats_mat))
n05ss_rnames <- c(rownames(n05ss_maucats_mat), setdiff(colnames(n05ss_maucats_mat), rownames(n05ss_maucats_mat)))

n05ss_maucats_mat <- cbind(rep(NA, nrow(n05ss_maucats_mat)),
                     n05ss_maucats_mat)
n05ss_maucats_mat <- rbind(n05ss_maucats_mat,
                     rep(NA, ncol(n05ss_maucats_mat)))

colnames(n05ss_maucats_mat) <- n05ss_cnames
rownames(n05ss_maucats_mat) <- n05ss_rnames
# dim(n05ss_maucats_mat)

n05ss_maucats_mat[lower.tri(n05ss_maucats_mat, diag = F)] <- 
    t(n05ss_maucats_mat)[lower.tri(n05ss_maucats_mat, diag = F)]

## just check everything is ok
# isSymmetric(n05ss_maucats_mat)
```

```{r} 
## compose a matrix for clustering and heatmap plotting
n10ss_maucats_mat <- as.matrix(data.frame(dcast(ss_maucats[SetSize == "N10"],
                                                method1 ~ method2, 
                                                value.var = "MeanAUCAT", 
                                                drop = F,
                                                fill = NA), 
                                          row.names = "method1"))

## N.B. only the upper/lower tringular of the matrix is
n10ss_maucats_mat <- n10ss_maucats_mat[sort(rownames(n10ss_maucats_mat)),
                                       sort(colnames(n10ss_maucats_mat))]

## add NA diagonal
n10ss_cnames <- c(setdiff(rownames(n10ss_maucats_mat), colnames(n10ss_maucats_mat)), colnames(n10ss_maucats_mat))
n10ss_rnames <- c(rownames(n10ss_maucats_mat), setdiff(colnames(n10ss_maucats_mat), rownames(n10ss_maucats_mat)))

n10ss_maucats_mat <- cbind(rep(NA, nrow(n10ss_maucats_mat)),
                           n10ss_maucats_mat)
n10ss_maucats_mat <- rbind(n10ss_maucats_mat,
                     rep(NA, ncol(n10ss_maucats_mat)))

colnames(n10ss_maucats_mat) <- n10ss_cnames
rownames(n10ss_maucats_mat) <- n10ss_rnames
# dim(n10ss_maucats_mat)

n10ss_maucats_mat[lower.tri(n10ss_maucats_mat, diag = F)] <- 
    t(n10ss_maucats_mat)[lower.tri(n10ss_maucats_mat, diag = F)]

## just check everything is ok
# isSymmetric(n05ss_maucats_mat)
```

## Heatmaps {.tabset}

### Not clustered

```{r, fig.width=8, fig.height=8} 
## check visually with a heatmap, without any method rearrangement
pheatmap::pheatmap(maucats_mat, 
                   main = "Area under concordance at the 100 top ranked DECs",
                   scale = "none",
                   color = viridis(255, option = "B"),
                   cluster_cols = F, 
                   cellwidth = 10, cellheight = 10,
                   cluster_rows = F)
```

### Not clustered N05

```{r, fig.width=8, fig.height=8} 
## check visually with a heatmap, without any method rearrangement
pheatmap::pheatmap(n05ss_maucats_mat, 
                   main = "Area under concordance at the 100 top ranked DECs in N05 data sets",
                   scale = "none",
                   color = viridis(255, option = "B"),
                   cluster_cols = F, 
                   cellwidth = 10, cellheight = 10,
                   cluster_rows = F)
```

### Clustered

```{r} 
## compute clustering of the methods according to AUCAT: the larger the AUCAT 
## between methods, the more similar the methods.
## Use dendsort to improve visualization

# maucats_clust <- hclust(as.dist(1 - maucats_mat))
maucats_clust <- dendsort(hclust(as.dist(1 - maucats_mat)))
# maucats_clust <- reorder(hclust(as.dist(1 - maucats_mat)), 
#                          as.dist(1 - maucats_mat),
#                          method = "OLO")
# plot(maucats_clust)

# maucats_clust
labels_clust_order <- maucats_clust$labels[maucats_clust$order]
```

```{r, fig.width=8.5, fig.height=8.5} 
pheatmap::pheatmap(maucats_mat, 
                   main = "Area under concordance at the 100 top ranked DECs",
                   color = viridis(255, option = "B"), 
                   # cutree_rows = 6, cutree_cols = 6,
                   cellwidth = 10, cellheight = 10,
                   cluster_cols = maucats_clust,
                   cluster_rows = maucats_clust)
```


```{r, fig.width=8.5, fig.height=8.5} 
# pheatmap::pheatmap(maucats_mat, 
#                    scale = "none",
#                    color = viridis(255, option = "B"),
#                    cellwidth = 10, cellheight = 10,
#                    cluster_cols = T,
#                    cluster_rows = T)
```

### Clustered N05

```{r} 
## compute clustering of the methods according to AUCAT: the larger the AUCAT 
## between methods, the more similar the methods.
## Use dendsort to improve visualization

# maucats_clust <- hclust(as.dist(1 - n05ss_maucats_mat))
# n05ss_maucats_clust <- dendsort(hclust(as.dist(1 - n05ss_maucats_mat)))
# n05ss_maucats_clust <- reorder(hclust(as.dist(1 - n05ss_maucats_mat)), 
#                                as.dist(1 - n05ss_maucats_mat),
#                                method = "OLO")
n05ss_maucats_clust <- seriate(as.dist(1 - n05ss_maucats_mat), method = "OLO")[[1]]
class(n05ss_maucats_clust) <- "hclust"
# plot(n05ss_maucats_clust)

# maucats_clust
n05ss_labels_clust_order <- n05ss_maucats_clust$labels[n05ss_maucats_clust$order]
```

```{r, fig.width=8.5, fig.height=8.5} 
pheatmap::pheatmap(n05ss_maucats_mat, 
                   main = "Area under concordance at the 100 top ranked DECs in N05 data sets",
                   color = viridis(255, option = "D"), 
                   # cutree_rows = 6, cutree_cols = 6,
                   cellwidth = 10, cellheight = 10,
                   cluster_cols = n05ss_maucats_clust,
                   cluster_rows = n05ss_maucats_clust)
```

### Clustered N10

```{r} 
n10ss_maucats_clust <- seriate(as.dist(1 - n10ss_maucats_mat), method = "OLO")[[1]]
class(n10ss_maucats_clust) <- "hclust"
# plot(n10ss_maucats_clust)

n10ss_labels_clust_order <- n10ss_maucats_clust$labels[n10ss_maucats_clust$order]
```

```{r, fig.width=8.5, fig.height=8.5} 
pheatmap::pheatmap(n10ss_maucats_mat, 
                   main = "Area under CAT ranked DECs in N05 data sets",
                   color = viridis(255, option = "D"), 
                   # cutree_rows = 6, cutree_cols = 6,
                   cellwidth = 10, cellheight = 10,
                   cluster_cols = n10ss_maucats_clust,
                   cluster_rows = n10ss_maucats_clust)
```

### Corrplot unclustered

```{r, fig.width=8.5, fig.height=8.5} 
corrplot::corrplot(maucats_mat, 
                   col = viridis(255, option = "D"),
                   type = "upper", 
                   is.corr = F, 
                   diag = F)
```

### Corrplot clustered

```{r, fig.width=8.5, fig.height=8.5} 
corrplot::corrplot(corr = maucats_mat[labels_clust_order, labels_clust_order], 
                   col = viridis(255, option = "D"),
                   type = "upper", 
                   is.corr = F, 
                   diag = F)
```

### Corrplot-like N05

```{r, fig.height=5.5, fig.width=5.5}
plot_dt <- melt(as.data.table(n05ss_maucats_mat, keep.rownames = "Method"), 
                id.vars = "Method", 
                variable.name = "Method2", 
                value.name = "AUCAT")

## compute the lower mat triangle pairs and erase the corresponding plot
halfmat <- n05ss_maucats_mat[n05ss_labels_clust_order, n05ss_labels_clust_order]
halfmat[upper.tri(halfmat, diag = T)] <- NA

halfmat_m <- melt(data.table(halfmat, keep.rownames = "method1"), 
                  id.vars = "method1", variable.name = "method2",
                  value.name = "concordance")[method1 != method2]
na_pairs <- halfmat_m[is.na(concordance), paste(method1, method2)]

plot_dt[, pairname := paste(Method, Method2)]
plot_dt[pairname %in% na_pairs, AUCAT := NA]

seqpal <- "YlGn"
# seqpal <- "YlOrRd"

n05_halfheat_plot <- 
    ggplot(plot_dt, aes(x = Method, y = Method2, 
                        color = AUCAT,
                        size = AUCAT,
                        fill = AUCAT)) +
    # geom_tile() +
    geom_point(shape = 21) +
    coord_fixed() +
    labs(x = NULL, y = NULL) +
    scale_size("Concordance\nat the top", range = c(0, 3), guide = "none") +
    # scale_fill_viridis_c(option = "B", end = .98, direction = 1) +
    # scale_color_viridis_c(option = "B", end = .98, direction = 1) +
    scale_fill_distiller("Concordance\nat the top", 
                         direction = 1, na.value = "white", palette = seqpal) +
    scale_color_distiller("Concordance\nat the top", 
                          direction = 1, na.value = "white", palette = seqpal) +
    guides(color = guide_colorbar(title.position = "top", title.hjust = .5, 
                                  frame.colour = "black"),
           fill  = guide_colorbar(title.position = "top", title.hjust = .5, 
                                  frame.colour = "black")) +
    scale_x_discrete(limits = n05ss_labels_clust_order, position = "bottom") +
    scale_y_discrete(limits = n05ss_labels_clust_order, position = "right") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, color = method_colors[n05ss_labels_clust_order]),
          axis.text.y = element_text(color = method_colors[n05ss_labels_clust_order]),
          legend.position = c(1.2, -.15),#"bottom",
          legend.direction = "horizontal", legend.text = element_text(angle = 90, hjust = 1),
          text = element_text(size = 9),
          panel.grid = element_blank())

n05_halfheat_plot
```

## AUCAT heat plot  {.tabset}

### All

```{r, fig.width=9, fig.height=8.5} 
plot_dt <- copy(mconc)

plot_dt <- 
    rbindlist(list(plot_dt, 
                   copy(plot_dt)[, tmp := method1][, .(method1 = method2, 
                                                       method2 = tmp, 
                                                       featFrac, 
                                                       concordance, 
                                                       AUCAT)]))

plot_dt$method1 <- factor(plot_dt$method1, 
                          levels = labels_clust_order,
                          ordered = T)

plot_dt$method2 <- factor(plot_dt$method2, 
                          levels = rev(labels_clust_order),
                          ordered = T)

aucat_heatplot <- 
  ggplot(plot_dt, aes(x = featFrac, y = concordance, fill = AUCAT)) +
  geom_area() +
  facet_grid(rows = vars(method1), cols = vars(method2), drop = F) +
  scale_fill_viridis() +
  # coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  theme_dendro() ## theme dendro removes almost everything

aucat_heatplot + 
  theme(legend.position = "left",
        strip.text.y = element_text(angle =  0, hjust = 0), #, colour = method_colors[rev(labels_clust_order)]
        strip.text.x = element_text(angle = 90, hjust = 0), #, colour = method_colors[labels_clust_order]
        strip.background = element_blank(),
        panel.spacing = unit(0, "cm"))
```

### N05

```{r, fig.width=9, fig.height=8.5} 
plot_dt <- copy(ss_mconc[SetSize == "N05"][, SetSize := NULL])

plot_dt <- 
    rbindlist(list(plot_dt, 
                   copy(plot_dt)[, tmp := method1][, .(method1 = method2, 
                                                       method2 = tmp, 
                                                       featFrac, 
                                                       concordance, 
                                                       AUCAT)]))

plot_dt$method1 <- factor(plot_dt$method1, 
                          levels = n05ss_labels_clust_order,
                          ordered = T)

plot_dt$method2 <- factor(plot_dt$method2, 
                          levels = rev(n05ss_labels_clust_order),
                          ordered = T)

n05_aucat_heatplot <- 
  ggplot(plot_dt, aes(x = featFrac, y = concordance, fill = AUCAT)) +
  geom_area() +
  facet_grid(rows = vars(method1), cols = vars(method2), drop = F) +
  scale_fill_viridis() +
  # coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  theme_dendro() ## theme dendro removes almost everything

n05_aucat_heatplot + 
  theme(legend.position = "left",
        strip.text.y = element_text(angle =  0, hjust = 0), #, colour = method_colors[rev(labels_clust_order)]
        strip.text.x = element_text(angle = 90, hjust = 0), #, colour = method_colors[labels_clust_order]
        strip.background = element_blank(),
        panel.spacing = unit(0, "cm"))
```

## AUCAT dendrogram {.tabset}

### All top

```{r, warning=FALSE, fig.width=5, fig.height=3}
ddata <- 
  dendro_data(as.dendrogram(maucats_clust, isReverse = T),
              type = "rectangle")

top_dendro <- 
  ggplot(segment(ddata), aes(x = x, y = y)) +
  geom_segment(aes(xend = xend, yend = yend)) +
  scale_x_continuous(name = NULL, 
                     trans = "reverse",
                     breaks = label(ddata)$x, 
                     labels = label(ddata)$label, 
                     expand = c(0, 0),
                     position = "bottom") +
  # scale_y_reverse(name = NULL, expand = c(0, 0.01)) +
  scale_y_continuous(name = NULL, expand = c(0, 0)) +
  coord_cartesian(xlim = c(.5, 38.5), expand = F) +
  # coord_flip() +
  # theme_minimal() +
  theme_dendro() +
  theme(axis.text.x = element_text(color = method_colors[label(ddata)$label], 
                                   angle = 90, hjust = 1, vjust = .5),
        # axis.text.y = element_text(angle = -35, hjust = .5, vjust = -1),
        axis.text.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

top_dendro
```

### All left

```{r, warning=FALSE, fig.width=3, fig.height=5}
left_dendro <- 
  ggplot(segment(ddata), aes(x = x, y = y)) +
  geom_segment(aes(xend = xend, yend = yend)) +
  scale_x_continuous(name = NULL, 
                     trans = "reverse",
                     breaks = label(ddata)$x, 
                     labels = label(ddata)$label, 
                     expand = c(0, 0),
                     position = "top") +
  scale_y_reverse(name = NULL, expand = c(0, 0)) +
  # scale_y_continuous(name = NULL, expand = c(0, 0.01)) +
  # coord_cartesian(xlim = c(.5, 38.5), expand = F) +
  coord_flip(xlim = c(.5, 38.5), expand = F) +
  # theme_minimal() +  
  theme_dendro() +
  theme(axis.text.y = element_text(color = method_colors[label(ddata)$label], 
                                   angle = 0, hjust = 1),
        # axis.text.x = element_text(angle = -35, hjust = .5, vjust = -1),
        axis.text.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

left_dendro
```

### N05 

```{r, warning=FALSE, fig.width=3, fig.height=5}
n05ss_ddata <- 
  dendro_data(as.dendrogram(n05ss_maucats_clust, isReverse = T),
              type = "rectangle")

n05ss_right_dendro <- 
  ggplot(segment(n05ss_ddata), aes(x = y, y = x)) +
  geom_segment(aes(xend = yend, yend = xend)) +
  scale_x_continuous(name = NULL, 
                     expand = c(0, 0),
                     position = "bottom") +
  # scale_y_reverse(name = NULL, expand = c(0, 0.01)) +
  scale_y_continuous(name = NULL, 
                     # trans = "reverse",
                     breaks = label(n05ss_ddata)$x, 
                     labels = label(n05ss_ddata)$label, 
                     expand = c(0, 0)) +
  coord_cartesian(ylim = c(.5, 38.5), expand = F) +
  theme_dendro() +
  theme(axis.text.y = element_text(color = method_colors[label(n05ss_ddata)$label]),
        # axis.text.y = element_text(angle = -35, hjust = .5, vjust = -1),
        axis.text.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

n05ss_right_dendro
```

### N05 dendro wrap

```{r, fig.height=5.5, fig.width=4.5}
method_order <- n05ss_labels_clust_order

## plot the average rank tile plot instead of the mean performance
n05_dendro_wrap <- 
    wrap_plots(plot_base_method_color_text +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.margin = unit(c(0, 0, 0, 0), "lines")),
               plot_base_method_type_tiles +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.background = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               n05ss_right_dendro + 
                   theme(axis.text.x = element_text(angle = 90, hjust = 1),
                         axis.text.y = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               nrow = 1, guides = "collect",
               widths = c(1.5, .1, 1)) & 
    theme(legend.position = "top",
          legend.key.size = unit(.7, "lines"),
          panel.spacing.x = unit(0, "lines"),
          panel.grid.minor = element_blank(),
          # plot.margin = margin(0.1, 0.1, 0.1, 0, "lines"),
          text = element_text(size = 10), 
          plot.tag = element_text(hjust = -1, vjust = -1, size = 12))

n05_dendro_wrap
```

### N10 dendro wrap

```{r, warning=FALSE, fig.width=3, fig.height=5}
n10ss_ddata <- 
  dendro_data(as.dendrogram(n10ss_maucats_clust, isReverse = T),
              type = "rectangle")

n10ss_right_dendro <- 
  ggplot(segment(n10ss_ddata), aes(x = y, y = x)) +
  geom_segment(aes(xend = yend, yend = xend)) +
  scale_x_continuous(name = NULL, 
                     expand = c(0, 0),
                     position = "bottom") +
  # scale_y_reverse(name = NULL, expand = c(0, 0.01)) +
  scale_y_continuous(name = NULL, 
                     # trans = "reverse",
                     breaks = label(n10ss_ddata)$x, 
                     labels = label(n10ss_ddata)$label, 
                     expand = c(0, 0)) +
  coord_cartesian(ylim = c(.5, 38.5), expand = F) +
  theme_dendro() +
  theme(axis.text.y = element_text(color = method_colors[label(n10ss_ddata)$label]),
        # axis.text.y = element_text(angle = -35, hjust = .5, vjust = -1),
        axis.text.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

# n10ss_right_dendro
```

```{r, fig.height=5.5, fig.width=4.5}
method_order <- n10ss_labels_clust_order

## plot the average rank tile plot instead of the mean performance
n10_dendro_wrap <- 
    wrap_plots(plot_base_method_color_text +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.margin = unit(c(0, 0, 0, 0), "lines")),
               plot_base_method_type_tiles +
                   scale_y_discrete(limits = method_order) +
                   theme(plot.background = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               n10ss_right_dendro + 
                   theme(axis.text.x = element_text(angle = 90, hjust = 1),
                         axis.text.y = element_blank(),
                         plot.margin = margin(0, 0, 0, 0, "lines")),
               nrow = 1, guides = "collect",
               widths = c(1.5, .1, 1)) & 
    theme(legend.position = "top",
          legend.key.size = unit(.7, "lines"),
          panel.spacing.x = unit(0, "lines"),
          panel.grid.minor = element_blank(),
          # plot.margin = margin(0.1, 0.1, 0.1, 0, "lines"),
          text = element_text(size = 10), 
          plot.tag = element_text(hjust = -1, vjust = -1, size = 12))

n10_dendro_wrap
```

## Combined plot {.tabset}

### All

```{r, fig.width=8, fig.height=7}
halfmat <- maucats_mat[labels_clust_order, labels_clust_order]
halfmat[lower.tri(halfmat, diag = T)] <- NA
halfmat_m <- melt(data.table(halfmat, keep.rownames = "method1"), 
                  id.vars = "method1", variable.name = "method2", 
                  value.name = "concordance")[method1 != method2]

na_pairs <- halfmat_m[is.na(concordance), paste(method1, method2)]

plot_dt <- copy(mconc)

plot_dt <- 
    rbindlist(list(plot_dt, 
                   copy(plot_dt)[, tmp := method1][, .(method1 = method2, 
                                                       method2 = tmp, 
                                                       featFrac, 
                                                       concordance, 
                                                       AUCAT)]))
plot_dt[, pairname := paste(method1, method2)]

plot_dt[pairname %in% na_pairs, concordance := NA]

plot_dt$method1 <- factor(plot_dt$method1, 
                          levels = labels_clust_order,
                          ordered = T)

plot_dt$method2 <- factor(plot_dt$method2, 
                          levels = rev(labels_clust_order),
                          ordered = T)

aucat_half_heatplot <- 
  ggplot(plot_dt, aes(x = featFrac, y = concordance, fill = AUCAT)) +
  geom_area() +
  facet_grid(rows = vars(method1), cols = vars(method2), drop = F) +
  scale_fill_viridis() +
  # coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = F) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1), expand = F) +
  theme_dendro() + ## theme dendro removes almost everything
  theme(legend.position = c(.8, .5), #"right",
        # strip.text = element_blank(),
        strip.background = element_blank(),
        panel.spacing = unit(.1, "lines"), 
        plot.margin = unit(c(-.5, -.5, -1, -.5), "lines"))
        # plot.margin = unit(c(0, -3, -1, -3), "lines"))
```


```{r, fig.width=9, fig.height=9}
##########
## data.table(method1 = labels_clust_order, method2 = labels_clust_order)
# ggplot(plot_dt[, .(x = .5, y = .5), by = .(method1, method2, AUCAT)], 
#        aes(x = x, y = y, color = AUCAT, size = AUCAT)) +
#   geom_point() +
#   facet_grid(rows = vars(method1), cols = vars(method2), drop = F) +
#   scale_color_viridis() +
#   coord_fixed(xlim = c(0, 1), ylim = c(0, 1), expand = F) +
#   theme_dendro() + ## theme dendro removes almost everything
#   theme(legend.position = c(.8, .5), 
#         strip.text = element_blank(), 
#         panel.border = element_rect(fill = NA, color = "red"),
#         plot.background = element_blank(),#element_rect(fill = NA, color = "gold", ),
#         strip.background = element_blank(),
#         panel.spacing = unit(.1, "lines"), 
#         plot.margin = unit(c(0, -3, -1, -3), "lines"))
```


```{r, fig.width=9, fig.height=8.5} 
# aucat_half_heatplot + 
#   theme(strip.text.y = element_text(angle =  0, hjust = 0),
#         strip.text.x = element_text(angle = 90, hjust = 0))
```


```{r, fig.width=8, fig.height=7}
# library(ggrastr)
# 
# rasterise(aucat_half_heatplot + 
#             theme(strip.text = element_blank()))
```


```{r, fig.width=9, fig.height=8.5} 
# expand.grid(unique(mconc$method1), unique(mconc$method1))

# void_square_plot <- 
#   ggplot(data.table(method1 = labels_clust_order, method2 = labels_clust_order), 
#          aes(x = method1, 
#              y = method2)) +
#   geom_point(size = NA) +
#   coord_fixed(expand = F, clip = "off") +
#   scale_y_discrete(expand = c(0, 0)) +
#   scale_x_discrete(position = "top", 
#                    expand = c(0, 0)) +
#   labs(x = NULL, y = NULL) +
#   # theme_dendro() +
#   theme(axis.text = element_blank(),
#         axis.ticks = element_blank(),
#         panel.border = element_rect(fill = NULL),
#         panel.spacing = unit(0, "lines"),
#         plot.background = element_rect(fill = "gold"),
#         plot.margin = unit(c(0, 0 ,0 ,0), "lines"))
# 
# void_square_plot <- 
#   # ggplot(unique(mconc[, .(method1, method2)]), 
#   ggplot(data.table(method1 = seq_along(labels_clust_order), 
#                     method2 = seq_along(labels_clust_order)),
#          aes(x = "1", y = "1")) +
#   # geom_point(size = 1) +
#   geom_raster() +
#   coord_fixed(expand = T, clip = "off") +
#   scale_y_discrete() +
#   scale_x_discrete(position = "top") +
#   labs(x = NULL, y = NULL) +
#   facet_grid(rows = vars(method1), cols = vars(method2)) +
#   # theme_dendro() +
#   theme(axis.text = element_blank(),
#         axis.ticks = element_blank(),
#         # panel.border = element_rect(fill = "gray"),
#         panel.spacing = unit(0, "lines"),
#         # plot.background = element_rect(fill = "gold"),
#         plot.margin = unit(c(0, 0 ,0 ,0), "lines"))
```


```{r, fig.width=9, fig.height=9} 
# design <- "
#   #1
#   23
# "
design <- "#1\n23"

top_dendro +
  left_dendro + 
  wrap_elements(rasterise(aucat_half_heatplot + 
                            theme(strip.text = element_blank(),
                                  plot.margin = margin(0, 0, 0, 0, "lines"))), 
                clip = F) + 
  # wrap_elements(panel = rasterise(void_square_plot)) + 
  plot_layout(design = design, 
              widths = c(1, 4), 
              heights = c(1, 4)) &
    theme(text = element_text(size = 9))
```

### N05 heatmap + dendro

```{r, fig.width=10.5, fig.height=7}
wrap_plots(n05_halfheat_plot +
               theme(#legend.position = "bottom",
                     axis.text.y = element_blank(), 
                     # axis.text.x = element_blank(), 
                     plot.margin = margin(0, 0, 0, 0)),
           n05_dendro_wrap &
               theme(legend.position = "bottom",
                     plot.margin = margin(0, 0, 0, 0),
                     plot.background = element_blank()),
           nrow = 1, 
           widths = c(2, 1.75)) 
```

# Session info

```{r}
sessionInfo()
```

