---
title: "Evaluate benchmark results comparing all datasets"
author: "Enrico Gaffo"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(SummarizedBenchmark)

library(R.utils)
library(data.table)
library(qs)
library(DT)
library(ComplexHeatmap)
library(scales)
library(ggplot2)

library(ggrepel)

library(BiocParallel)

library(ROCR)

nWorkers <- multicoreWorkers()
```

```{r}
## output file path
output_dir <- "overall_evaluations"
dir.create(path = output_dir, showWarnings = F, recursive = T)

# ## input data
# adj_eval_metrics_files <- file.path(c("DM1_evaluations", 
#                               "IPF_evaluations",
#                               "MS_evaluations",
#                               "IDC_evaluations"), 
#                             "adj_eval_metrics.csv.gz")
# 
# adj_eval_metrics_dt <- rbindlist(lapply(adj_eval_metrics_files, fread), idcol = "Source")
```

```{r}
if(file.exists(file.path(output_dir, "sbAssay_dt.csv.gz"))){
    input_dt <- file.path(output_dir, "sbAssay_dt.csv.gz")
    sbAssay_all_dt <- fread(input_dt)
}else{
    sumBench_perf_metrics_qs_files <- file.path(c("DM1_performance",
                                                  "IPF_performance",
                                                  "MS_performance",
                                                  "IDC_performance"), 
                                                "sumBench_perf_metrics.qs")
    
    names(sumBench_perf_metrics_qs_files) <- sub("_performance", "",
                                                 dirname(sumBench_perf_metrics_qs_files))
    
    ## read input: the list of the SummarizedBenchmark objects after the performance evaluation 
    ncpus <- 50
    bpparam <- BatchtoolsParam(workers = length(sumBench_perf_metrics_qs_files), 
                               saveregistry = F,
                               cluster = "slurm",
                               resources = list(ncpus = ncpus, 
                                                walltime = 7200, # 2h max
                                                memory = 1000) #64GB
    )
    
    sbL <- bplapply(sumBench_perf_metrics_qs_files, 
                    qs::qread, 
                    nthreads = ncpus,  #multicoreWorkers()
                    BPPARAM = bpparam)
    
    sbAssay_all_dt <- 
        rbindlist(lapply(sbL,
                         function(sbL){
                             rbindlist(lapply(sbL, 
                                              function(x){
                                                  data.table(as.data.frame(colData(x)), 
                                                             keep.rownames = "Method")
                                              }), 
                                       idcol = "Dataset")[, c("SetSize", "MZP", "DsType", 
                                                              "DsId") := tstrsplit(Dataset, "_")]
                         }
        ), 
        idcol = "Source_ds")
    
    fwrite(sbAssay_all_dt, file.path(output_dir, "sbAssay_dt.csv.gz"))
}
```

```{r}
alpha_targets <- c(0.01, 0.05, 0.1) 
```

# DE data sets

```{r}
sbAssay_dt <- sbAssay_all_dt[DsType == "de" & MZP == "bulk"]
```

## Performance {.tabset}

```{r}
setnafill(x = sbAssay_dt, 
          type = "const", 
          fill = 1, 
          nan = NA, 
          cols = grep("FDR", colnames(sbAssay_dt), value = T))
```

```{r}
value_cols <- 
  c(grep("rejections", colnames(sbAssay_dt), value = T),
    grep("TPR", colnames(sbAssay_dt), value = T),
    grep("TNR", colnames(sbAssay_dt), value = T),
    grep("FDR", colnames(sbAssay_dt), value = T))

msbAssay_dt <- 
  sbAssay_dt[, lapply(.SD, mean, na.rm = T), 
           .SDcols = value_cols,
           by = .(Source_ds, SetSize, MZP, DsType, Method)]
```

```{r}
show_dt <- copy(msbAssay_dt)
show_dt$Source_ds <- factor(show_dt$Source_ds)
show_dt$SetSize <- factor(show_dt$SetSize)
show_dt$MZP <- factor(show_dt$MZP)
show_dt$DsType <- factor(show_dt$DsType)
show_dt$Method <- factor(show_dt$Method)

datatable(show_dt, 
          caption = paste("Alphas:", paste(alpha_targets, collapse = "/")),
          rownames = F, 
          filter = "top") %>%
  formatRound(value_cols, 3)
```

```{r}
plot_dt <- melt(msbAssay_dt[DsType == "de" & MZP == "bulk"], 
                id.vars = c("Source_ds", "SetSize", "MZP", "DsType", "Method"))
```

### Recall (TPR)

```{r}
# pval_tpr_pattern <- "^TPR.[0-9]$"
padj_tpr_pattern <- "^TPR.[0-9].[0-9]$"
tpr_pattern <- padj_tpr_pattern #pval_tpr_pattern
Alpha_plot_label <- "P-value \U2264"
if(tpr_pattern == padj_tpr_pattern){
  Alpha_plot_label <- "P-adj \U2264"
}
```

```{r, fig.width=10}
## Avg TPR
ggplot(plot_dt[grep(tpr_pattern, variable)], ## get P-values TPRs
       aes(x = Method, y = value)) +
  geom_line(aes(group = factor(Source_ds), color = factor(Source_ds))) +
  geom_point(aes(shape = factor(Source_ds), color = factor(Source_ds))) +
  ylab("Average recall") +
  # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
  # scale_shape_discrete(Alpha_plot_label, labels = alpha_targets) +
  facet_grid(cols = vars(SetSize), 
             rows = vars(variable), scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
        legend.position = "top")
```

### Precision (1-FDR)

```{r}
pval_fdr_pattern <- "^FDR.[0-9]$"
padj_fdr_pattern <- "^FDR.[0-9].[0-9]$"
fdr_pattern <- padj_fdr_pattern #pval_fdr_pattern
Alpha_plot_label <- "P-value \U2264"
if(fdr_pattern == padj_fdr_pattern){
  Alpha_plot_label <- "P-adj \U2264"
}
```

```{r, fig.width=10}
## Avg Precision
ggplot(plot_dt[grep(fdr_pattern, variable)], ## get P-values TPRs
       aes(x = Method, y = 1 - value)) +
  geom_line(aes(group = factor(Source_ds), color = factor(Source_ds))) +
  geom_point(aes(shape = factor(Source_ds), color = factor(Source_ds))) +
  ylab("Average precision") +
  # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
  # scale_shape_discrete(Alpha_plot_label, labels = alpha_targets) +
  facet_grid(cols = vars(SetSize), 
             rows = vars(variable), scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
        legend.position = "top")
```

## {-}
### F-scores

```{r}
## auxiliary functions

simple_auc <- function(TPR, FPR){
    # inputs already sorted, best scores first 
    dFPR <- c(diff(FPR), 0)
    dTPR <- c(diff(TPR), 0)
    sum(TPR * dFPR) + sum(dTPR * dFPR)/2
}

## can be used to compute F1 and other F-scores, such as F0.5 (beta = 0.5)
f.beta <- function(P, R, beta = 1) {
    (1 + beta^2) * ( (P * R) / ( (beta^2 * P) + R) )
}

## compute F1 score from precision and recall
f1 <- function(P, R) {
    # 2 * ((P * R)/(P + R))
    f.beta(P, R, beta = 1)
}
```

```{r, fig.width=10}
## F1-score
ds_id_cols <- c("Source_ds", "SetSize", "MZP", "DsType", "Method", "DsId", "Dataset")

f1s <- 
  merge(melt(sbAssay_dt[, c(ds_id_cols,
                          grep(fdr_pattern, colnames(sbAssay_dt), value = T)), with = F], 
             id.vars = ds_id_cols, 
             value.name = "FDR",
             variable.name =  "Alpha")[, Alpha := sub("FDR.", "", Alpha)][],
        melt(sbAssay_dt[, c(ds_id_cols,
                          grep(tpr_pattern, colnames(sbAssay_dt), value = T)), with = F], 
             id.vars = ds_id_cols, 
             value.name = "TPR",
             variable.name = "Alpha")[, Alpha := sub("TPR.", "", Alpha)][],
        by = c(ds_id_cols, "Alpha"))

f1s[, `:=`(F1 = f1(1 - FDR, TPR),
           F0.5 = f.beta(1 - FDR, TPR, .5))] 

## add the number of rejections
# rej_pattern <- "^rejections.[0-9]$" #P-vals
rej_pattern <- "^rejections.[0-9].[0-9]$" #Padj

f1s <- 
  merge(f1s, 
        melt(sbAssay_dt[, c(ds_id_cols,
                          grep(rej_pattern, colnames(sbAssay_dt), value = T)), with = F], 
             id.vars = ds_id_cols, 
             value.name = "rejections",
             variable.name = "Alpha")[, Alpha := sub("rejections.", "", Alpha)][],
        by = c(ds_id_cols, "Alpha"))

f1s[is.nan(F1), F1 := 0]
f1s[is.nan(F0.5), F0.5 := 0]
```

```{r}
## compute mean values
mf1s <- f1s[, .(F1 = mean(F1, na.rm = T),
                sdF1 = sd(F1, na.rm = T),
                F0.5 = mean(F0.5, na.rm = T),
                sdF0.5 = sd(F0.5, na.rm = T),
                TPR = mean(TPR, na.rm = T),
                sdTPR = sd(TPR, na.rm = T),
                FDR = mean(FDR, na.rm = T),
                sdFDR = sd(FDR, na.rm = T),
                rejections = mean(rejections, na.rm = T)), 
            by = .(Source_ds, SetSize, MZP, DsType, Method, Alpha)]
```

```{r}
show_dt <- copy(mf1s)
show_dt$Source_ds <- factor(show_dt$Source_ds)
show_dt$SetSize <- factor(show_dt$SetSize)
show_dt$MZP <- factor(show_dt$MZP)
show_dt$DsType <- factor(show_dt$DsType)
show_dt$Method <- factor(show_dt$Method)
show_dt$Alpha <- factor(show_dt$Alpha)

datatable(show_dt, rownames = F, filter = "top") %>%
  formatRound(c("F1", "sdF1", 
                "F0.5", "sdF0.5", 
                "TPR", "sdTPR", 
                "FDR", "sdFDR", 
                "rejections"), 3)
```

#### F1 {.tabset} 

##### Boxplots

```{r, fig.width=7, fig.height=15}
ggplot(f1s, 
       aes(x = Method, y = F1)) +
    geom_boxplot(aes(color = Source_ds), 
                 outlier.size = .5) +
    ylab("F1") +
    # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
    facet_grid(cols = vars(SetSize), rows = vars(paste(MZP, Alpha)), scales = "free_y") +
    coord_flip() +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

##### Average line plot

```{r, fig.width=10}
plot_dt <- mf1s[, c("baseMethod", "Params", "Test") := tstrsplit(Method, "_")]
plot_dt$Method <- gsub("_", " ", plot_dt$Method)

ggplot(plot_dt, 
       aes(x = Method, y = F1)) +
    geom_line(aes(group = Source_ds, color = Source_ds)) +
    geom_boxplot(aes(group = Method), alpha = .7,
                 # fill = NA, 
                 outlier.shape = NA) +
    geom_point(aes(shape = Source_ds, color = Source_ds)) +
    ylab("Average F1") +
    # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
    # scale_shape_discrete(Alpha_plot_label, labels = alpha_targets) +
    facet_grid(cols = vars(SetSize), 
               rows = vars(Alpha), scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

##### Average point line plot

```{r, fig.width=10}
plot_dt <- 
    mf1s[, c("baseMethod", "Params", 
             "Test") := tstrsplit(Method, 
                                  "_")][, .(AvgF1 = mean(F1),
                                            SdF1 = sd(F1)), 
                                        by = .(SetSize, MZP, DsType, Method, Alpha)]
plot_dt$Method <- gsub("_", " ", plot_dt$Method)
```

```{r, fig.width=10}
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

method_colors <- setNames(gg_color_hue(length(unique(plot_dt$Method))), 
                          unique(plot_dt$Method))
```

```{r, fig.width=10}
plot_dt$Method <- factor(plot_dt$Method, 
                         levels = plot_dt[SetSize == "N03" & 
                                              Alpha == "2.1"][order(AvgF1), Method], 
                         ordered = T)

p0.05N03 <- 
    ggplot(plot_dt[SetSize == "N03"], 
           aes(x = Method, y = AvgF1)) +
    geom_line(aes(group = "1"), color = "grey", linetype = "solid") +
    geom_errorbar(aes(ymin = AvgF1 - SdF1, ymax = AvgF1 + SdF1), 
                  color = "grey45",
                  width = 0.5) +
    geom_point(aes(color = Method)) +
    scale_color_manual(values = method_colors, guide = NULL) +
    ylab("Average F1") +
    facet_grid(cols = vars(SetSize), 
               rows = vars(Alpha), scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

```{r, fig.width=10}
plot_dt$Method <- factor(plot_dt$Method, 
                         levels = plot_dt[SetSize == "N05" & 
                                              Alpha == "2.1"][order(AvgF1), Method], 
                         ordered = T)

p0.05N05 <- 
    ggplot(plot_dt[SetSize == "N05"], 
           aes(x = Method, y = AvgF1)) +
    geom_line(aes(group = "1"), color = "grey", linetype = "solid") +
    geom_errorbar(aes(ymin = AvgF1 - SdF1, ymax = AvgF1 + SdF1), 
                  color = "grey45",
                  width = 0.5) +
    geom_point(aes(color = Method)) +
    scale_color_manual(values = method_colors, guide = NULL) +
    ylab("Average F1") +
    facet_grid(cols = vars(SetSize), 
               rows = vars(Alpha), scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

```{r, fig.width=10}
plot_dt$Method <- factor(plot_dt$Method, 
                         levels = plot_dt[SetSize == "N10" & 
                                              Alpha == "2.1"][order(AvgF1), Method], 
                         ordered = T)

p0.05N10 <- 
    ggplot(plot_dt[SetSize == "N10"], 
           aes(x = Method, y = AvgF1)) +
    geom_line(aes(group = "1"), color = "grey", linetype = "solid") +
    geom_errorbar(aes(ymin = AvgF1 - SdF1, ymax = AvgF1 + SdF1), 
                  color = "grey45",
                  width = 0.5) +
    geom_point(aes(color = Method)) +
    scale_color_manual(values = method_colors, guide = NULL) +
    ylab("Average F1") +
    facet_grid(cols = vars(SetSize), 
               rows = vars(Alpha), scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

```{r, fig.width=10}
library(patchwork)

result <- 
    p0.05N03 + labs(x = NULL, y = NULL) + coord_cartesian(ylim = c(0, 1)) +
    theme(strip.background.y = element_blank(), strip.text.y = element_blank(), 
          plot.margin = unit(c(0, 0, 0, 0), "lines")) +
    p0.05N05 + labs(x = NULL, y = NULL) + coord_cartesian(ylim = c(0, 1)) +
    theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
          strip.background.y = element_blank(), strip.text.y = element_blank(), 
          plot.margin = unit(c(0, 0, 0, 0), "lines")) +
    p0.05N10 + labs(x = NULL, y = NULL) + coord_cartesian(ylim = c(0, 1)) +
    theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), 
          plot.margin = unit(c(0, 0, 0, 0), "lines"))

gt <- patchwork::patchworkGrob(result)
gridExtra::grid.arrange(gt, left = "Avg F1", bottom = "Method")
```

#### F0.5 {.tabset} 

##### Boxplot

```{r, fig.width=7, fig.height=15}
ggplot(f1s, 
       aes(x = Method, y = F0.5)) +
    geom_boxplot(aes(color = Source_ds), 
                 outlier.size = .5) +
    ylab(expression(F[0.5])) +
    # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
    facet_grid(cols = vars(SetSize), rows = vars(paste(MZP, Alpha)), scales = "free_y") +
    coord_flip() +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

##### Average lineplot

```{r, fig.width=10}
plot_dt <- mf1s[, c("baseMethod", "Params", "Test") := tstrsplit(Method, "_")]
plot_dt$Method <- gsub("_", " ", plot_dt$Method)

ggplot(plot_dt, 
       aes(x = Method, y = F0.5)) +
    geom_line(aes(group = Source_ds, color = Source_ds)) +
    geom_boxplot(aes(group = Method), alpha = .7,
                 # fill = NA, 
                 outlier.shape = NA) +
    geom_point(aes(shape = Source_ds, color = Source_ds)) +
    ylab(expression(Average~F[0.5])) +
    # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
    # scale_shape_discrete(Alpha_plot_label, labels = alpha_targets) +
    facet_grid(cols = vars(SetSize), 
               rows = vars(Alpha), scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
          legend.position = "top")
```

## FDR vs TPR {.tabset}

```{r}
x.breaks <- sort(c(.01, .05, seq(0, 1, by = .1)))
```

### Custom average (all methods) Bulk

```{r}
# fdrtpr_curve <-
#     rbindlist(lapply(split(adj_pval_deind_dt, 
#                            by = c("SetSize", "MZP", "DsType", "Method")), 
#                      function(x){
#                          as.data.table(get_avg_meas(x[, .(Dataset, true_val,
#                                                           preds)]))
#                      }), 
#               idcol = "DS_meth")
# 
# # fdrtpr_curve[is.na(FDR), FDR := 1]
# # fdrtpr_curve[is.na(TPR), TPR := 0]
# 
# fdrtpr_curve[, c("SetSize", "MZP", "DsType", "Method") := tstrsplit(DS_meth, "\\."), 
#         by = DS_meth]
# 
# alpha_fdrtpr_curve <- 
#     rbindlist(list("0.1" = fdrtpr_curve[order(Cutoff)][Cutoff <= .1, 
#                                           lapply(.SD, tail, 1), 
#                                           by = DS_meth],
#                    "0.05" = fdrtpr_curve[order(Cutoff)][Cutoff <= .05, 
#                                           lapply(.SD, tail, 1), 
#                                           by = DS_meth],
#                    "0.01" = fdrtpr_curve[order(Cutoff)][Cutoff <= .01, 
#                                           lapply(.SD, tail, 1), 
#                                           by = DS_meth]), 
#               idcol = "Alpha")
```

```{r, fig.height=7, fig.width=12}
# ggplot(fdrtpr_curve[MZP == "bulk"][order(Cutoff)], 
#        aes(x = FDR, y = TPR, color = Method)) +
#     geom_vline(xintercept = .01, linetype = 2, color = "grey25") +
#     geom_vline(xintercept = .05, linetype = 2, color = "grey25") +
#     geom_vline(xintercept = .1, linetype = 2, color = "grey25") +
#     geom_path() + 
#     geom_point(data = alpha_fdrtpr_curve[MZP == "bulk" & (Cutoff > FDR)], 
#                size = 3, aes(shape = Alpha, fill = Method), show.legend = F) +
#     geom_point(data = alpha_fdrtpr_curve[MZP == "bulk" & (Cutoff <= FDR)], 
#                size = 3, aes(shape = Alpha), fill = "white") +
#     scale_shape_manual("P-adj \U2264", values = 21:23) +
#     facet_grid(cols = vars(SetSize),
#                rows = vars(MZP)) +
#     scale_x_continuous(breaks = x.breaks, 
#                        labels = c("", tail(x.breaks, -1))) +
#     guides(color = guide_legend(nrow = 3, title.position = "top"),
#            shape = guide_legend(nrow = 3, title.position = "top")) +
#     coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
#     labs(y = "Average TPR", x = "Average FDR") +
#     theme_bw() +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5), 
#           panel.grid.major.y = element_blank(), 
#           panel.grid.minor.y = element_blank(), 
#           panel.grid.major.x = element_line(linetype = 2, color = "grey75"),
#           panel.grid.minor.x = element_blank(),
#           legend.position = "top")
```

White fill points when P-adj > empirical FDR   

## Precision-recall curve {.tabset}

### Custom average (all methods) Bulk

```{r}
# pr_curve <-
#     rbindlist(lapply(split(adj_pval_deind_dt, 
#              by = c("SetSize", "MZP", "DsType", "Method")), 
#        function(x){
#            as.data.table(get_avg_meas(x[, .(Dataset, true_val, 
#                                             preds = 1 - preds)][order(preds)], 
#                                       meas.a = "tpr", 
#                                       meas.b = "ppv"))
#        }), 
#        idcol = "DS_meth")[, Cutoff := 1 - Cutoff]
# 
# pr_curve[, c("SetSize", "MZP", "DsType", "Method") := tstrsplit(DS_meth, "\\."), 
#         by = DS_meth]
# 
# alpha_pr_curve <- 
#     rbindlist(list("0.1" = pr_curve[order(Cutoff)][Cutoff <= .1, 
#                                           lapply(.SD, tail, 1), 
#                                           by = DS_meth],
#                    "0.05" = pr_curve[order(Cutoff)][Cutoff <= .05, 
#                                           lapply(.SD, tail, 1), 
#                                           by = DS_meth],
#                    "0.01" = pr_curve[order(Cutoff)][Cutoff <= .01, 
#                                           lapply(.SD, tail, 1), 
#                                           by = DS_meth]), 
#               idcol = "Alpha")
```

```{r, fig.height=7, fig.width=12}
# ggplot(pr_curve[MZP == "bulk"][order(Cutoff)], 
#        aes(x = TPR, y = PPV, color = Method)) +
#     geom_line() +
#     geom_point(data = alpha_pr_curve[MZP == "bulk" & (Cutoff > (1 - PPV))], 
#                size = 3, aes(shape = Alpha, fill = Method), show.legend = F) +
#     geom_point(data = alpha_pr_curve[MZP == "bulk" & (Cutoff <= (1 - PPV))], 
#                size = 3, aes(shape = Alpha), fill = "white") +
#     scale_shape_manual("P-adj \U2264", values = 21:23) +
#     facet_grid(cols = vars(SetSize),
#                rows = vars(MZP)) +
#     guides(color = guide_legend(nrow = 3, title.position = "top"),
#            shape = guide_legend(nrow = 3, title.position = "top")) +
#     coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
#     labs(x = "Average TPR", y = "Average PPV") +
#     theme_bw() +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
#           legend.position = "top")
```

White fill points when P-adj > empirical FDR   

## ROC (FPR vs TPR) {.tabset}

```{r}
# get_auc <- function(y) {
#     
#     y_preds <- lapply(split(y[, .(Dataset, preds)], 
#                             by = "Dataset", 
#                             keep.by = F, 
#                             drop = T), 
#                       function(x)x$preds)
#     y_labels <- lapply(split(y[, .(Dataset, true_val)], 
#                              by = "Dataset", 
#                              keep.by = F, 
#                              drop = T), 
#                        function(x)x$true_val)
#     
#     rocr_pred <- ROCR::prediction(predictions = y_preds,
#                                   labels = y_labels)
#     
#     ROCR::performance(rocr_pred, measure = "auc")@y.values
# }
```

### P-values ROCR bulk

```{r}
# plot_dt <-
#     rbindlist(lapply(split(pval_deind_dt, 
#              by = c("SetSize", "MZP", "DsType", "Method")), 
#        function(x){
#            as.data.table(get_avg_meas(x[, .(GeneID = seq_along(true_val),
#                                             true_val,
#                                             preds = 1 - preds),
#                                         by = Dataset], 
#                                       meas.a = "tpr", 
#                                       meas.b = "fpr"))
#        }), idcol = "DS_meth")
# plot_dt[, c("SetSize", "MZP", "DsType", "Method") := tstrsplit(DS_meth, "\\."), 
#         by = DS_meth]
```

```{r, fig.height=7.5, fig.width=5}
# ggplot(plot_dt[MZP == "bulk"][order(Cutoff)], 
#        aes(x = PPV, y = TPR, color = Method)) +
#     geom_abline(slope = 1, linetype = 2) +
#     geom_line() + 
#     facet_grid(rows = vars(SetSize),
#                cols = vars(MZP)) +
#     guides(color = guide_legend(ncol = 1)) +
#     coord_fixed() +
#     labs(y = "Average TPR", x = "Average FPR") +
#     theme_bw() +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

```{r}
## AUC values
evaluations_dirs <- c("DM1_evaluations",
                      "IPF_evaluations",
                      "IDC_evaluations",
                      "MS_evaluations")
pval_ROC_AUC_files <- file.path(evaluations_dirs,
                                "pval_ROC_AUC.csv")
names(pval_ROC_AUC_files) <- sub("_evaluations", "", dirname(pval_ROC_AUC_files))
pval_ROC_AUC <- rbindlist(lapply(pval_ROC_AUC_files,
                          fread), idcol = "Source_ds")[MZP == "bulk" & DsType == "de"]
```

```{r}
mean_pval_ROC_AUC <- pval_ROC_AUC[, .(AUC = mean(AUC, na.rm = T),
                            sdAUC = sd(AUC, na.rm = T),
                            seAUC = sqrt(var(AUC, na.rm = T)/length(AUC))),
                            by = .(Source_ds, SetSize, MZP, DsType,
                                   Method = as.character(Method))]
```

#### AUC ROCR boxplot

```{r, fig.width=10}
plot_dt <- pval_ROC_AUC
mean_plot_dt <- mean_pval_ROC_AUC

ggplot(plot_dt, aes(x = Method, y = AUC)) +
    geom_boxplot(outlier.size = .5) +
    geom_point(data = mean_plot_dt, 
             shape = 21, fill = "red") +
    facet_grid(cols = vars(SetSize),
               rows = vars(Source_ds), 
               scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

#### AUC ROCR pointrange

```{r, fig.width=10}
ggplot(mean_plot_dt, aes(x = Method, y = AUC)) +
  geom_line(aes(group = paste(Source_ds, SetSize, MZP, DsType), color = Source_ds)) +
  # geom_point(shape = 21, fill = "red") +
  geom_pointrange(aes(ymin = AUC - sdAUC, ymax = AUC + sdAUC, fill = Source_ds),
                  # position = position_dodge(width = .5), 
                  # alpha = .5,
                  shape = 21) +
  ylab("Average AUC (FDR, TPR)") +
  facet_grid(cols = vars(SetSize),
             # rows = vars(MZP), 
             scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
        legend.position = "top")
```

#### AUC ROCR table

```{r}
show_dt <- copy(mean_plot_dt)
show_dt$SetSize <- factor(show_dt$SetSize)
show_dt$MZP <- factor(show_dt$MZP)
show_dt$DsType <- factor(show_dt$DsType)
show_dt$Method <- factor(show_dt$Method)

datatable(show_dt, rownames = F, filter = "top") %>%
  formatRound(c("AUC", "sdAUC", "seAUC"), 3)
```

### Adjusted P-values ROCR bulk

```{r}
# plot_dt <-
#     rbindlist(lapply(split(adj_pval_deind_dt, 
#              by = c("SetSize", "MZP", "DsType", "Method")), 
#        function(x){
#            # message(paste(unique(x$SetSize), unique(x$MZP), unique(x$Method)))
#            as.data.table(get_avg_meas(x[, .(GeneID = seq_along(true_val),
#                                             true_val,
#                                             preds = 1 - preds),
#                                         by = Dataset], 
#                                       meas.a = "tpr", 
#                                       meas.b = "fpr"))
#        }), idcol = "DS_meth")[order(Cutoff)]
# plot_dt[, c("SetSize", "MZP", "DsType", "Method") := tstrsplit(DS_meth, "\\."), 
#         by = DS_meth]
```

```{r, fig.height=7.5, fig.width=5}
# ggplot(plot_dt[MZP == "bulk"], 
#        aes(x = PPV, y = TPR, color = Method)) +
#     geom_abline(slope = 1, linetype = "dashed") +
#     geom_line() + 
#     facet_grid(rows = vars(SetSize),
#                cols = vars(MZP)) +
#     # scale_x_continuous(breaks = x.breaks, 
#     #                    labels = c("", tail(x.breaks, -1))) +
#     guides(color = guide_legend(ncol = 1)) +
#     coord_fixed() +
#     labs(y = "Average TPR", x = "Average FPR") +
#     theme_bw() +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

#### AUC ROCR boxplot

```{r}
padj_ROC_AUC_files <- file.path(evaluations_dirs, "padj_ROC_AUC.csv")
names(padj_ROC_AUC_files) <- sub("_evaluations", "", dirname(padj_ROC_AUC_files))
padj_ROC_AUC <- rbindlist(lapply(padj_ROC_AUC_files,
                                 fread), 
                          idcol = "Source_ds")[MZP == "bulk" & DsType == "de"]
```

```{r}
## AUC values
mean_padj_ROC_AUC <- 
    padj_ROC_AUC[, .(AUC = mean(AUC, na.rm = T),
                           sdAUC = sd(AUC, na.rm = T),
                           seAUC = sqrt(var(AUC, na.rm = T) / length(AUC))),
                       by = .(Source_ds, SetSize, MZP, DsType,
                              Method = as.character(Method))]
```

```{r, fig.width=10}
plot_dt <- padj_ROC_AUC
mean_plot_dt <- mean_padj_ROC_AUC

ggplot(plot_dt, aes(x = Method, y = AUC)) +
    geom_boxplot(outlier.size = .5) +
    geom_point(data = mean_plot_dt, 
             shape = 21, fill = "red") +
    facet_grid(cols = vars(SetSize),
               rows = vars(Source_ds), 
               scales = "free_y") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

#### AUC ROCR pointrange

```{r, fig.width=10}
ggplot(mean_plot_dt, aes(x = Method, y = AUC)) +
  geom_line(aes(group = paste(Source_ds, SetSize, MZP, DsType), color = Source_ds)) +
  # geom_point(shape = 21, fill = "red") +
  geom_pointrange(aes(ymin = AUC - sdAUC, ymax = AUC + sdAUC, fill = Source_ds),
                  # position = position_dodge(width = .5), 
                  # alpha = .5,
                  shape = 21) +
  ylab("Average AUC (FDR, TPR)") +
  facet_grid(cols = vars(SetSize),
             # rows = vars(MZP), 
             scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
        legend.position = "top")
```

#### AUC ROCR table

```{r}
show_dt <- copy(mean_plot_dt)
show_dt$SetSize <- factor(show_dt$SetSize)
show_dt$MZP <- factor(show_dt$MZP)
show_dt$DsType <- factor(show_dt$DsType)
show_dt$Method <- factor(show_dt$Method)

datatable(show_dt, rownames = F, filter = "top") %>%
  formatRound(c("AUC", "sdAUC", "seAUC"), 3)
```

# Running times

```{r, fig.width=10}
plot_dt <- sbAssay_dt[, Seconds := ifelse(grepl("_ZW_", Method), Runtime.2, Runtime.1)]

method_names <- sort(unique(plot_dt$Method))
method_colors <- setNames(hue_pal()(length(method_names)), method_names)

plot_dt$Method <- factor(plot_dt$Method, 
                         levels = plot_dt[, .(Mtime = mean(Seconds)), 
                                          by = Method][order(Mtime), unique(Method)], 
                         ordered = T)

ggplot(plot_dt, 
       aes(x = Method, y = Seconds, color = Method)) +
  geom_boxplot(outlier.size = .5) +
  facet_grid(cols = vars(SetSize),
             rows = vars(MZP)) +
  scale_color_manual(values = method_colors, guide = "none") +
  scale_y_log10("Runtime (mm:ss)", 
                breaks = c(0.1, 1, 10, 60, 600),
                labels = c("00:00.1", "00:01", "00:10", "01:00", "10:00")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, 
                                   color = method_colors[levels(plot_dt$Method)]))
```

```{r, fig.width=10, fig.height=7}
plot_dt <- 
  merge(mf1s, 
        sbAssay_dt[, .(mTime = mean(Seconds)), by = .(SetSize, MZP, Method)],
        by = c("SetSize", "MZP", "Method"))


ggplot(plot_dt, aes(x = F1, y = mTime, color = Method, shape = baseMethod)) +
  geom_point() +
  facet_grid(cols = vars(SetSize),
             rows = vars(MZP, Alpha), 
             scales = "free") +
  scale_y_log10("Runtime (mm:ss)", 
                breaks = c(0.1, 1, 10, 60, 600),
                labels = c("00:00.1", "00:01", "00:10", "01:00", "10:00")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

```{r, fig.width=10, fig.height=7}
ggplot(plot_dt, aes(x = F0.5, y = mTime, color = Method, shape = baseMethod)) +
  geom_point() +
  facet_grid(cols = vars(SetSize),
             rows = vars(MZP, Alpha), 
             scales = "free") +
  scale_y_log10("Runtime (mm:ss)", 
                breaks = c(0.1, 1, 10, 60, 600),
                labels = c("00:00.1", "00:01", "00:10", "01:00", "10:00")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

# Mock data set

```{r}
sbAssay_dt <- sbAssay_all_dt[MZP == "bulk" & DsType == "mock"]
```

## Performance {.tabset}

```{r}
## FPR = 1 - TNR
setnafill(x = sbAssay_dt, 
          type = "const", 
          fill = 0, 
          nan = NA, 
          cols = grep("TNR", colnames(sbAssay_dt), value = T))
```

```{r}
value_cols <- 
  c(grep("rejections", colnames(sbAssay_dt), value = T),
    # grep("TPR", colnames(sbAssay_dt), value = T),
    # grep("FDR", colnames(sbAssay_dt), value = T),
    grep("TNR", colnames(sbAssay_dt), value = T))

msbAssay_dt <- 
  sbAssay_dt[, lapply(.SD, mean, na.rm = T), 
           .SDcols = value_cols,
           by = .(Source_ds, SetSize, MZP, DsType, Method)]
```

```{r}
show_dt <- copy(msbAssay_dt)
show_dt$SetSize <- factor(show_dt$SetSize)
show_dt$MZP <- factor(show_dt$MZP)
show_dt$DsType <- factor(show_dt$DsType)
show_dt$Method <- factor(show_dt$Method)

datatable(show_dt, 
          caption = paste("Alphas:", paste(alpha_targets, collapse = "/")),
          rownames = F, 
          filter = "top") %>%
  formatRound(value_cols, 3)
```

```{r}
plot_dt <- melt(msbAssay_dt, id.vars = c("Source_ds", "SetSize", "MZP", "DsType", "Method"))
```

### FPR

```{r}
pval_tnr_pattern <- "^TNR.[0-9]$"
padj_tnr_pattern <- "^TNR.[0-9].[0-9]$"
tnr_pattern <- pval_tnr_pattern #padj_tnr_pattern
Alpha_plot_label <- "P-value \U2264"
if(tnr_pattern == padj_tnr_pattern){
  Alpha_plot_label <- "P-adj \U2264"
}
```

```{r, fig.width=10}
## Avg FPR = 1 - TNR
ggplot(plot_dt[grep(tnr_pattern, variable)], 
       aes(x = Method, y = 1 - value)) +
  geom_line(aes(group = Source_ds, color = Source_ds)) +
  geom_point(aes(shape = Source_ds, color = Source_ds)) +
  ylab("Average FPR") +
  # scale_color_discrete(Alpha_plot_label, labels = alpha_targets) +
  # scale_shape_discrete(Alpha_plot_label, labels = alpha_targets) +
  facet_grid(cols = vars(SetSize), 
             rows = vars(variable),
             scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
        legend.position = "top")
```

# Session info

```{r}
sessionInfo()
```

